### 2016-12-23 doc/chap-1-foreword.tex

>>>>

For debugging purpose, you can first add a configuration like this:

\begin{enumerate}
\item Go to \verb!Run -> Edit Configurations!
\item Click the ``+'' button on the left to add a new configuration, select ``Remote'' in the drop-down menu
\item Name the configuration something like ``remote-debugging'', then it should work out of box (you can check that the port is 5005 though)
\item Save the configuration by clicking ``OK''
\end{enumerate}

Now you can debug by first launching SAFE with a \verb!-debug! flag as the first argument, then following your other options. For example, \verb!./bin/safe -debug analyze something.js!. Your application is supposed to wait for connection from debugger once started, then you can start the debugging configuration we just created in IntelliJ.
